\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{RGB}{230,230,250}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\newcommand{\blank}[1]{\hspace*{#1}}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\indent  \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.5in} l @{\hskip 0.6in} l @{\hskip 0.75in} l @{\hskip 1in} l }
\hline
\textbf{Examination} & \textbf{University} & \textbf{Institute } & \textbf{Year} & \textbf{CPI/\%} \\
\hline
Graduation      & IIT Bombay & IIT Bombay & 2020 & 8.96 \\
Intermediate/+2 & CBSE & KV NERIST, Nirjuli   & 2016 & 97.6\%\\
Matriculation & CBSE & KV NERIST, Nirjuli & 2014 & 10\\
\hline
\end{tabular}
\\ \\
\indent \indent Pursuing Minor in \textbf{Computer Science} \\
\indent \indent GitHub - \href{https://github.com/thechargedneutron}{https://github.com/thechargedneutron}
%\end{center}
%\end{table}
\\

\resheading {\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Neural Networks, Machine Learning, Information Theory, Image Processing
\end{itemize}

\resheading{\textbf{ACADEMIC ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.05em}
\item \noindent Qualified \textbf{Indian National Mathematical Olympiad} and got into \textbf{top 30} at the Indian selection camp for the \textbf{International Mathematical Olympiad}'15.
\item \noindent Achieved \textbf{99.97 percentile} (out of 1.2 million candidates) in \textbf{JEE Mains 2016} and \textbf{99.14 percentile} (out of 0.2 million candidates) in \textbf{JEE Advanced 2016}.
\item \noindent Awarded \textbf{Certificate of Merit} for getting into State wise Top 1\% in the preliminaries for the \textbf{Indian National Chemistry Olympiad}, \textbf{Indian National Physics Olympiad} and \textbf{Indian National Astronomy Olympiad}.
\item \noindent Secured full marks \textbf{(100/100)} in Computer Science and Chemistry in Intermediate \textbf{AISSCEE examination}. Also scored the highest in the entire \textbf{North Eastern Region}
\end{itemize}

\resheading{\textbf{AWARDS AND SCHOLARSHIPS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.05em}
\item \noindent Received \emph{Rashtrapati Puraskar} (\textbf{President's Award}) for excellence in interdisciplinary activities, by \textbf{The Hon'ble President of India.}
\item \noindent Witnessed \textbf{Republic Day Parade - 2017} from the \textbf{PM Box} as a guest of \textbf{Hon'ble Prime Minister}, for academic excellence in High School.
\item \noindent Awarded \textbf{Dera Natung Scholarship} for securing top State rank in AISSCEE examination.
\item \noindent Received \textbf{Kishore Vyaganik Protsahan Yojana Scholarship} award to pursue research in \textbf{Basic Sciences}.
\item \noindent Recipient of \textbf{National Talent Search Scholarship} meant to identify and nurture talent in High School.
\end{itemize}

\resheading{\textbf{WORK EXPERIENCE} }\\[\lsep]
\begin{itemize}
\item \textbf{Open Source Contribution
}  \\
 \emph{(\textbf{Scikit-learn}, Python Library for Machine Learning)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Contributing to Scikit-learn with a globally distributed workforce of engineers.
	
	\item Contributed towards the codebase of the organization.
.
	\item Introduced and modified various features, including 

	\end{itemize}

\item \textbf{GUI for OpenModelica} \\
 \emph{(Prof. Kannan Moudgalya 
, FOSSEE, India)} \blank{7.5cm} \emph{May'17 to July'17} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Developed GUI in Kivy (Python) for OpenModelica, a chemical simulator, as a part of \emph{Free and Open Source Software for Education}, an initiative of IIT Bombay and MHRD, Govt. of India.
	\item Linked the existing OpenModelica with the developed GUI and made it user friendly.
	\end{itemize}
\end{itemize}


\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}
\item  \textbf{Handwritten Language Translator} \\
 \emph{Self Project}
 \begin{itemize}\itemsep \isep
 \item Developed \textbf{Neural Network} model in \textbf{scikit-learn} to recognize Handwritten letters.
 \item Built a \textbf{GUI} in Python to take user input and process letters.
 \item Currently trained and deployed in \textbf{Hindi} and \textbf{Engish}, easily implementable to other languages.
 \end{itemize}
\end{itemize}

\resheading{\textbf{LEADERSHIP AND RESPONSIBILITY} }\\[\lsep]
\begin{itemize}
\item \textbf{Web and Coding Club, IIT Bombay - \emph{Convener} 
}  \\
 \emph{Apr'17 - Present} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Organized and hosted events pertaining to Coding and Web Development.
.
	\item Demonstrated various programming essentials, including git, GitHub and Android Development.

	\item Mentored projects including \textbf{Attendance App} and \textbf{SIFT}(Scale Invariant Feature Transform).

	\end{itemize}

\item \textbf{Electrical Engineering Students' Association, IIT Bombay - \emph{Joint Secretary}
}  \\
 \emph{ Mar'17 - Present} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Coordinated with Faculty members and students to conduct department events including excursion.
	\item Second subitem.
	\end{itemize}

\item \textbf{\emph{Class Representative}, Electrical Engineering, IIT Bombay
}  \\
 \emph{ Aug'16 - Present} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Coordinated with Faculty members to schedule classes and tutorials.
	\item Developed a notion of unity among classmates and batch mates.
	\item Introduced Intradepartment Football match.
	\end{itemize}
\end{itemize}

\resheading{\textbf{KEY COURSES} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.1em}
\item \noindent \textbf{Electrical Engineering} - Electronic Devices, Network Theory, Data Analysis and Interpretation, Introduction to Electrical Systems, Introduction to Electronics
\item \noindent \textbf{Computer Sciences} - Computer Networks, Basic Programming and Utilization
\item \noindent \textbf{Mathematics} - Complex Analysis, Calculus, Linear Algebra, Differential Equations
\item \noindent \textbf{Miscellaneous} - Quantum Physics and Application, Electricity and Magnetism

\end{itemize}

\resheading{\textbf{EXTRA CURRICULAR} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0.1em}
\item \noindent LECTURE ON MATHS
\item \noindent Part of the Kho-Kho camp for the 
\item \noindent Represented state in \textbf{Kho-Kho} at the \textbf{42nd KVS National Sports Meet}, Chandigarh.


\end{itemize}

\end{document}


